---
title: "Lecture Notes"
author: "Mike Talbot"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: TRUE
    number_sections: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)

# Config parameters
envname <- "cive580c3"
packages <- c("python=3.11", 
              "pip", 
              "numpy", 
              "matplotlib", 
              "pandas", 
              "geopandas", 
              "rasterstats")

# Install Miniconda (first time only)
#install_miniconda(force = F)

# Create environment (first time only)
#conda_remove(envname, packages = NULL, conda = "auto") # remove env if necessary
#conda_create(envname, forge = T, packages = packages) # create new env
#conda_list(conda = "auto") # check that the new env is listed

# Use the new environment for reticulate
use_miniconda(envname)
```

## Load dependencies
```{python load-dependencies}
import os
import numpy as np
import pandas as pd
import geopandas as gpd
import matplotlib
from matplotlib import pyplot as plt
import rasterstats
from rasterstats import zonal_stats
import rasterio
from rasterio.warp import transform_bounds, calculate_default_transform, reproject, Resampling
from scipy.stats import linregress
from contextlib import redirect_stdout

# Define common CRS to use
output_crs = "OGC:CRS83"
```

## 2025-01-28
No notes.

## 2025-01-30
- Swath width is a function of the instantaneous field of view (IFOV) - the angle through which a sensor is receiving electromagnetic radiation.

```{r q1}
ifov <- 3.54E-4 #radians
height <- 700 #km
# tan(ifov / 2) = (width / 2) / height
width <- 2 * height * tan(ifov / 2) * 1000 #m
print(width)
```

- Bandwidth and central wavelength affect spatial resolution
- Full Width Half Bandwidth (FWHB) is often referenced
- Atmospheric transmission of different wavelengths affects spatial resolution
- For rainfall, infrared can really only measure the cloud top, while microwave can sense hydrometeors (within the cloud)

## 2025-02-04
- GPM has both passive and active microwave
- Measures different types of precipitation at difference frequencies
- DRP sends out two different frequencies: 35 GHz and 13.6 GHz
  - Perpendicular to flight: range
  - Parallel to flight: azimuth

## 2025-02-11
Guest lecture by Gabriel Senay
- ET is a response variable, whereas precipitation is a driver
- FANO equation is intended to estimate the theoretical wet bulb temperature for a landsat image
- 